Implementation of poloidal density variation in collision operator

### 2019-04-30 doc/manual/version3/inputParameters.tex
Added adjoint and ambipolar options to manual.

{\ttfamily RHSMode} = 3: Solve for the 2$\times$2 monoenergetic transport coefficients. When this option is chosen, \Nx~is set to 1, only 1 species is used and \parlink{includePhi1} is set to \false
}

@@

@@

{\ttfamily geometryScheme}==12: Read the IPP {\ttfamily .bc} format Boozer-coordinate file specified in \parlink{equilibriumFile} below. 
The file is assumed to be stellarator-\emph{asymmetric}.
}

@@

@@

>>>>

{\ttfamily RHSMode} = 3: Solve for the 2$\times$2 monoenergetic transport coefficients. When this option is chosen, \Nx~is set to 1, only 1 species is used and \parlink{includePhi1} is set to \false \\

{\ttfamily RHSMode} = 4: Solve the adjoint equation to compute derivatives at constant $E_r$. Options related to the adjoint solve are detailed in section \ref{sec:adjointOptions}. {\ttfamily RHSMode} = 4 must be used with \\ \parlink{includePhi1}=\false, \parlink{EParallelHat}\texttt{=0}, \parlink{magneticDriftScheme}\texttt{>0}, \\ \parlink{constraintScheme}\texttt{=-1} or 1, \parlink{collisionOperator}\texttt{=0}, and \parlink{geometryScheme}\texttt{/=5}. \\

{\ttfamily RHSMode} = 5: Solve the adjoint equation to compute derivatives at the ambipolar $E_r$. Options related to the adjoint solve are detailed in section \ref{sec:adjointOptions}. {\ttfamily RHSMode} = 5 must be used with \\ \parlink{includePhi1}=\false, \parlink{EParallelHat}\texttt{=0}, \parlink{magneticDriftScheme}\texttt{>0}, \\ \parlink{constraintScheme}\texttt{=-1} or 1, \parlink{collisionOperator}\texttt{=0}, and \parlink{geometryScheme}\texttt{/=5}. \\ 
}

@@

\param{ambipolarSolve}
{Boolean}
{\false}
{When \parlink{RHSMode}==1, 4, or 5.}
{When \true, a root finding method will be used to find the ambipolar \parlink{Er}. All output parameters will be included at the ambipolar \parlink{Er}. Options related to this parameter are \parlink{NEr\_ambipolarSolve}, \parlink{Er\_search\_tolerance\_dx}, \parlink{Er\_search\_tolerance\_f}, \\ \parlink{ambipolarSolveOption}, \parlink{Er\_min}, and \parlink{Er\_max}.}

\param{NEr\_ambipolarSolve}
{integer}
{20}
{When \parlink{ambipolarSolve} == \true.}
{Maximum number of solves to allow while finding the ambipolar \parlink{Er}.}

\param{Er\_search\_tolerance\_dx}
{real}
{1.d-8}
{When \parlink{ambipolarSolve} == \true and \parlink{ambipolarSolveOption}/=2.}
{Tolerance used for ambipolar solve. If step size in \parlink{Er} falls below \parlink{Er\_search\_tolerance\_dx}, the ambipolar solve completes successfully. Note that this is not used for \parlink{ambipolarSolveOption}==2.}

\param{Er\_search\_tolerance\_f}
{real}
{1.d-10}
{When \parlink{ambipolarSolve} == \true.}
{Tolerance used for ambipolar solve. If the radial current,
\begin{gather}
J_r = \sum_s \texttt{Zs}(s) \texttt{particleFlux\_vm\_rN}(s),
\end{gather}
falls below \parlink{Er\_search\_tolerance\_f}, the ambipolar solve completes successfully.}

\param{ambipolarSolveOption}
{integer}
{1}
{When \parlink{ambipolarSolve} == \true}
{Indicates which root solving algorithm to use for ambipolar solve. \\
\parlink{ambipolarSolveOption}==1: a Newton bisection method is used \\ 
\parlink{ambipolarSolveOption}==2: a Brent method is used \\
\parlink{ambipolarSolveOption}==3: a Newton method is used.

If \parlink{ambipolarSolveOption}==1 or 3, an adjoint method will used to compute the $\partial J_r/\partial E_r$, so must be used with \parlink{includePhi1}==\false, \parlink{EParallelHat}==0, \parlink{magneticDriftScheme}$>0$, \parlink{constraintScheme}==-1 or 1, and \parlink{collisionOperator}==0.}

\param{Er\_min}
{real}
{-100}
{When \parlink{ambipolarSolve} == \true and \parlink{ambipolarSolveOption} /= 3. }
{Minimum value of \parlink{Er} used to bracket the ambipolar root. }

\param{Er\_max}
{real}
{100}
{When \parlink{ambipolarSolve} == \true and \parlink{ambipolarSolveOption} /= 3. }
{Maximum  value of \parlink{Er} used to bracket the ambipolar root. }

@@

{\ttfamily geometryScheme}==12: Read the IPP {\ttfamily .bc} format Boozer-coordinate file specified in \parlink{equilibriumFile} below. 
The file is assumed to be stellarator-\emph{asymmetric}.

{\ttfamily geometryScheme}==13: Read Boozer geometry from the {\ttfamily geometryParamters} namelist. Here the geometry parameters are specified by \parlink{Nperiods}, \parlink{boozer\_bmnc}, \parlink{GHat}, \parlink{IHat}, and \parlink{iota}. This has been implemented for use with STELLOPT for direct optimization of the Boozer spectrum. 
}

@@

\param{boozer\_bmnc}
{2D array of reals}
{0}
{Only when \parlink{geometryScheme} == 13. }
{Fourier harmonics describing the magnetic field in Boozer coordinates,
\begin{gather}
B(\theta_B,\zeta_B) = \sum_{m,n}\mathrm{\texttt{boozer\_bmnc}}(m,n) \cos(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B) + \mathrm{\texttt{boozer\_bmnc}}(m,n) \sin(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B),
\end{gather}
The first index of \texttt{ Boozer\_bmnc} corresponds to $m \in $[0,40], and the second corresponds to $n \in $[-40,40]. Here \parlink{Nperiods} can be specified in the input file.
}

\param{boozer\_bmns}
{2D array of reals}
{0}
{Only when \parlink{geometryScheme} == 13. }
{Fourier harmonics describing the magnetic field in Boozer coordinates,
\begin{gather}
B(\theta_B,\zeta_B) = \sum_{m,n}\mathrm{\texttt{boozer\_bmnc}}(m,n) \cos(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B) + \mathrm{\texttt{boozer\_bmnc}}(m,n) \sin(m\theta_B-n\mathrm{\texttt{Nperiods}} \zeta_B),
\end{gather}
The first index of \texttt{ Boozer\_bmns} corresponds to $m \in $[0,40], and the second corresponds to $n \in $[-40,40]. Here \parlink{Nperiods} can be specified in the input file.
}

\param{Nperiods}
{integer}
{0}
{Only when \parlink{geometryScheme} == 13.}
{Boozer geometry will assume number of periods is \texttt{Nperiods}.}

@@

\section{The \texttt{adjointOptions} namelist}
\label{sec:adjointOptions}

This namelist allows for derivatives of the outputs to be computed with respect to geometric parameters. If \parlink{RHSMode}\texttt{<4}, this namelist will not be read.

\param{adjointBootstrapOption}
{Boolean}
{\false}
{When \parlink{RHSMode} == 4 or 5}
{If this parameter is \true, the derivative of the bootstrap current (\parlink{FSABjHatOverRootFSAB2}) is computed with respect to geometry parameters: \parlink{GHat}, \parlink{IHat}, \parlink{iota}, and \parlink{bmnc}.}

\param{adjointRadialCurrentOption}
{Boolean}
{\false}
{When \parlink{RHSMode} == 4 or 5}
{If this parameter is \true the derivative of the radial current,
\begin{gather}
J_r = \sum_s \texttt{Zs}(s) \texttt{particleFlux\_vm\_rN}(s),
\end{gather}
is computed with respect to geometry parameters: \parlink{GHat}, \parlink{IHat}, \parlink{iota}, and \parlink{bmnc}. Here \parlink{Zs} and \parlink{particleFlux\_vm\_rN} can be found elsewhere in this document.}

\param{adjointTotalHeatFluxOption}
{Boolean}
{\false}
{When \parlink{RHSMode} == 4 or 5}
{If this parameter is \true, the derivative of the total heat flux,
\begin{gather}
Q = \sum_s \texttt{heatFlux\_vm\_rN}(s),
\end{gather}
is computed with respect to geometry parameters: \parlink{GHat}, \parlink{IHat}, \parlink{iota}, and \parlink{bmnc}. Here \parlink{heatFlux\_vm\_rN} can be found elsewhere in this document.}

\param{adjointHeatFluxOption}
{1D array of booleans}
{\false}
{When \parlink{RHSMode} == 4 or 5}
{This array is the same length as {\ttfamily nHats} and other species parameters. If parameter is \true, the derivative of the heat flux (\parlink{heatFlux\_vm\_rN}) will be computed for this species with respect to geometry parameters: \parlink{GHat}, \parlink{IHat}, \parlink{iota}, and \parlink{bmnc}.}

\param{adjointParticleFluxOption}
{1D array of booleans}
{\false}
{When \parlink{RHSMode} == 4 or 5}
{This array is the same length as {\ttfamily nHats} and other species parameters. If parameter is \true, the derivative of the particle flux (\parlink{particleFlux\_vm\_rN}) will be computed for this species with respect to geometry parameters: \parlink{GHat}, \parlink{IHat}, \parlink{iota}, and \parlink{bmnc}.}

\param{adjointParallelFlowOption}
{1D array of booleans}
{\false}
{When \parlink{RHSMode} == 4 or 5}
{This array is the same length as {\ttfamily nHats} and other species parameters. If parameter is \true, the derivative of the parallel flow (\parlink{FSABVelocityUsingFSADensityOverRootFSAB2}) will be computed for this species with respect to geometry parameters: \parlink{GHat}, \parlink{IHat}, \parlink{iota}, and \parlink{bmnc}.}

\param{discreteAdjointOption}
{boolean}
{\true}
{When \parlink{RHSMode} == 4 or 5}
{When \parlink{RHSMode} is \true, the discrete adjoint technique is used. If \false, the continuous technique is used. Both should give the same result within discretization error, but the discrete approach should be slightly faster.
}

\param{nMaxAdjoint}
{integer}
{0}
{When \parlink{RHSMode} == 4 or 5}
{Derivatives of outputs specified by \parlink{adjointBootstrapOption}, \\ \parlink{adjointRadialCurrentOption}, \parlink{adjointTotalHeatFluxOption}, \\ \parlink{adjointHeatFluxOption}, \parlink{adjointParticleFluxOption}, and \\ \parlink{adjointParallelFlowOption} will computed for Fourier modes $|n| \leq $ \texttt{nMaxAdjoint}. }

\param{mMaxAdjoint}
{integer}
{0}
{When \parlink{RHSMode} == 4 or 5}
{Derivatives of outputs specified by \parlink{adjointBootstrapOption}, \\ \parlink{adjointRadialCurrentOption}, \parlink{adjointTotalHeatFluxOption}, \\ \parlink{adjointHeatFluxOption}, \parlink{adjointParticleFluxOption}, and \\ \parlink{adjointParallelFlowOption} will computed with respect to \parlink{bmnc} for Fourier modes $m \leq $ \texttt{mMaxAdjoint}. }

\param{nMinAdjoint}
{integer}
{0}
{When \parlink{RHSMode} == 4 or 5}
{Derivatives of outputs specified by \parlink{adjointBootstrapOption}, \\ \parlink{adjointRadialCurrentOption}, \parlink{adjointTotalHeatFluxOption}, \\ \parlink{adjointHeatFluxOption}, \parlink{adjointParticleFluxOption}, and \\ \parlink{adjointParallelFlowOption} will computed with respect to \parlink{bmnc} for Fourier modes $|n| \geq $ \texttt{nMaxAdjoint}. }

\param{mMinAdjoint}
{integer}
{0}
{When \parlink{RHSMode} == 4 or 5}
{Derivatives of outputs specified by \parlink{adjointBootstrapOption}, \\ \parlink{adjointRadialCurrentOption}, \parlink{adjointTotalHeatFluxOption}, \\ \parlink{adjointHeatFluxOption}, \parlink{adjointParticleFluxOption}, and \\ \parlink{adjointParallelFlowOption} will computed with respect to \parlink{bmnc} for Fourier modes $m \geq $ \texttt{mMaxAdjoint}. }

\param{debugAdjoint}
{boolean}
{\false}
{When \parlink{RHSMode} == 4 or 5. }
{If \texttt{.true.}, then derivatives computed with the adjoint method will be compared with forward difference derivatives with step size set by \parlink{deltaLambda}.}

\param{deltaLambda}
{real}
{1.d-4}
{When \parlink{deltaLamda} == \texttt{.true.}}
{The step size used for forward difference derivatives will be \texttt{deltaLambda} multiplied by the quantity that is being varied. For example, the step size for a Boozer harmonic, $B_{mn}$, would be $\Delta B_{mn} = $\texttt{deltaLambda}$B_{mn}$.}
